\documentclass[letterpaper,11pt]{article}
\usepackage[utf8]{inputenc}

\title{CV Jair Alfredo Cueto Angulo}
\author{Jair Alfredo Cueto Angulo}
\date{January 2022}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    {\Huge \scshape Jair Alfredo Cueto Angulo} \\ \vspace{1pt}
    Campo Sabancuy No. 218-B Frac. Carrizal, Villahermosa, Tabasco, México. CP: 86038 \\ \vspace{1pt}
    \small \raisebox{-0.1\height}\faPhone\  (+52) 937-593-32-90 ~ \href{mailto:x@gmail.com}{\raisebox{-0.2\height}\faEnvelope\  \underline{jair.cueto25@outlook.com}} ~ 
    \href{https://linkedin.com/in//}{\raisebox{-0.2\height}\faLinkedin\ \underline{linkedin.com/in/jair-cueto}}  ~
    \href{https://github.com/}{\raisebox{-0.2\height}\faGithub\ \underline{github.com/jaircueto}}
    \vspace{-8pt}
\end{center}

%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {\href{https://www.udg.mx/}{Universidad de Guadalajara (UDG)}
}{Sep 2020 - Present}
      {Master of Science in Geophysics;  GPA: (93.91/100.00)}{Puerto Vallarta, Jalisco}
      \\ \vspace{7.5pt}
      {Thesis: Analysis of the statistical properties of seismicity in Los Humeros Volcanic Complex (LHVC)} \\
      {Advisor: PhD Claudia Beatriz M. Quinteros Cartaya}  \\ 
      {Relevant Coursework: Time Series Analysis, Seismology I, GIS I, Geostatistics, GMT and Inversion Theory} \\
      {Awards: CONACYT Postgraduate Scholarship in Mexico}
    \resumeSubheading
      {\href{https://www.ujat.mx//}{University Júarez Autonomous of Tabasco (UJAT)}}{Jul 2013 - Dec 2018}
      {Bachelor of Engineering in Geophysics;  GPA: (8.46/10.0)}{Cunduacán, Tabasco}
      \\ \vspace{7.5pt}
      {Relevant Coursework: Geophysical Modeling, Seismology, Seismic and Electrical Prospecting, Oil seismic data processing, Petrophysics and Geophysical records of wells.} \\
      {Awards: Social Service Scholarship} \textbar { Mexican Petroleum Institute}
  \resumeSubHeadingListEnd

%-----------EXPERIENCE-----------
\section{Work Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Sistemas de Información Geográfica S.A. de C.V.}{Mar 2020 - Sep 2020}
      {Geoanalysis Specialist}{Villahermosa, Tabasco}
      \\ \vspace{10pt}
      \resumeItemListStart
      {Developed of marine monitoring applications from Synthetic Aperture Radar (SAR) images:}
        \item{Detected marine objects, ships, oil spills and natural seeps.}
        \item{Estimated of ocean wind speed and direction.}
      \resumeItemListEnd

\resumeSubheading
      {Sistemas de Información Geográfica S.A. de C.V.}{Oct 2019 – Mar 2020}
      {Training in GIS}{Villahermosa, Tabasco}
      \\ \vspace{10pt}
      \resumeItemListStart
      {Designed and implementation of GIS solutions projects for Oil and Gas:}
        \item{Modeled of geological formations and oil well trajectory.}
        \item{Developed of geoprocess automation with Python Notebook in ArcGIS PRO.}
    \resumeItemListEnd

\resumeSubheading
     {Seismic Technology S.A. De C.V.}{Mar 2018 - Dec 2018}
      {Intership}{Villahermosa, Tabasco}
      \\ \vspace{10pt}
      \resumeItemListStart
      {2D land and marine seismic data processing:}
      \begin{multicols}{2}
            \begin{itemize}[itemsep=-5pt, parsep=3pt]
                \item Quality control (QC)
                \item Correction of residual statics
                \item Elimination of bubbles and phase adjustment
                \item Noise removal (coherent and random)
                \item Stacking speed model, RMS, time interval
                \item NMO correction
                \item Multiple attenuation (SRME, WEMA, Radon transform tau - rho)
            \end{itemize}
      \end{multicols}
    \resumeItemListEnd

  \resumeSubHeadingListEnd
\vspace{-16pt}

%-----------Academic Experience-----------
\section{Academic Experience}
\setlength\itemsep{-0.4em}
\textbf{1st Summer School “Principles of Earthquake Location and its Correlations \\ with Seismic Network Designs”} \hfill \textbf{Aug 16 - 20, 2021} \\ {International Association for Seismology and Physics of the Interior of the Earth (IASPEI)} \hfill \emph{Virtual mode}
\\ \vspace{8pt}

\textbf{XIX School of Probability and Statistics} \hfill \textbf{Apr 19 – 23, 2021} \\
{Center for Research in Mathematics, AC (CIMAT)} \hfill \emph{Guanajuato, Gto.}
\\ \vspace{8pt}

\textbf{President of the Student Chapter AMGE - UJAT} \hfill \textbf{Jan 2018 - Jan - 2019} \\
{Mexican Association of Exploration Geophysicists (AMGE)} \hfill \emph{Cunduacán, Tabasco}
 \begin{itemize}[leftmargin=0.15in, label={}]
 \item{
 \text{Organized of courses, workshops and conferences, related to the dissemination of research and application of geophysics. Consolidate alliances and strengthen relationships with associations, companies and other student chapters of Mexico.}
 }
 \end{itemize}
 
\textbf{Summer Scholarship of Scientific and Technological Research of the Pacific XXII} \hfill \textbf{Spring 2017} \\
{UNAM, Geosciences Center} \hfill \emph{Juriquilla, Querétaro}
\\ \vspace{8pt}

\textbf{Summer Scholarship of Scientific and Technological Research of the Pacific XXI} \hfill \textbf{Spring 2016} \\
{UDG, Center for Seismology and Volcanology of the West} \hfill \emph{Pto. Vallarta, Jalisco}
\vspace{-16pt}

%
%-----------Languages-----------
\section{Languages}
\begin{minipage}[t]{0.55\textwidth}
	
	\vspace{-0.5mm}
	\small \textbf{English} \hfill \hspace{-5pt}{\ssmall Intermediate: B2 Independent User \hfill \hspace{3pt}} \SkillBull{$\bullet \bullet \bullet \bullet \, \circ$}\\
	
	\vspace{-0.5mm}
	\small \textbf{Spanish} \hfill \hspace{-5pt}{\ssmall Native Competition \hfill \hspace{3pt}} \SkillBull{$\bullet \bullet \bullet \bullet \, \bullet$}
\end{minipage}

%
%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills and Interests}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \item{
     \textbf{Programming Languages}{:  Python, Matlab, R} \\
     \textbf{Seismic Processing / Interpretation:}{: ObsPy, Seismic Unix, OpenCPS, OpendTect, Petrel} \\
     \textbf{Mapping}{: GMT, QGIS, ArcGIS Pro, Surfer, Oasis Montaj} \\
     \textbf{Interests}{: Latin American Literature and Cult Movies} \\
    }
 \end{itemize}
 \vspace{-16pt}

%
%-----------Conferences and Presentations-----------
\section{Conferences and Presentations}
\begin{description}
	\raggedright
	\item {\textbf{J. Cueto}}, C. Quinteros, A. Figuero-Soto and M. Calò. (2021). {\it Resultados preliminares del análisis espacio - temporal de la sismicidad en el Complejo Volcánico Los Humeros (LHVC)}. Virtual Oral Presentation. Reunión Anual de la Unión Geofísica Mexicana (RAUGM).
	\item {\textbf{J. Cueto}}, L. Romero and V.H. Márquez-Ramírez. (2017). {\it Clasificación y procesamiento de datos sísmicos del volcán Ceboruco, Nayarit}. Poster presentation. VIII Congreso Nacional de Estudiantes de Ciencias de la Tierra (CNECT).
	\end{description}
 \vspace{-16pt}

%
%-----------Courses and Certifications-----------
\section{Courses and Certifications}
  \resumeSubHeadingListStart
      \resumeItemListStart
        \item{SAR Remote Sensing - Introductory Level} \textbar { National Commission for Space Activities} \textbar { ID: lSJ3PyUb2A}
        \item{Optical Remote Sensing - Introductory Level} \textbar { National Commission for Space Activities} \textbar { ID: U84EBVHP0o}
        \item{Understanding and Visualizing Data with Python} \textbar { University of Michigan} \textbar { ID: ZYRZC3FFK4QJ}
        \item{Seismic Data Analysis Basic Level} \textbar { National Seismological Service} \textbar { ID: 585}
        \item{Foundations of Data Science: K-Means Clustering in Python} \textbar { University of London} \textbar { ID: 88GNTBM873PH}
        \item{Introduction to the use and representation of geospatial information} \textbar { Center for Research in Geospatial Information Sciences}
        \item{Oil \& Gas From Exploration to Distribution} \textbar { Total, IFP School \& Fundación YPF}
        \item{RigPass: Onshore \& Offshore} \textbar { International Association of Drilling Contractors} \textbar { ID: SX000081358}
        \item{Oil \& Gas Industry Operations and Markets} \textbar { University Duke} \textbar { ID: 4DYRVZBG5ARN}
        \item{Spatial Data Science: The New Frontier in Analytics} \textbar { Environmental Systems Research Institute}
        \item{Cartography} \textbar { Environmental Systems Research Institute}
        \item{Introduction to geothermal} \textbar { National Autonomous University of Mexico} \textbar { ID: BB4F7NQU65WP}
        \item{The Dynamic Earth: A Course for Educators} \textbar { American Museum of Natural History} \textbar { ID: MH6LJTUQ8AKJ}
        \item{Oceanography: a key to better understand our world} \textbar { University of Barcelona} \textbar { ID: MD4C3NF7PRRE}
      \resumeItemListEnd
\vspace{-16pt}

%
%-----------PROFESSIONAL AFFILIATIONS-----------
\section{Professional Affilations}
 \begin{itemize}[leftmargin=0, label={}]
    \item{
     \textit{Member}{, \href{https://www.seismosoc.org/}{Seismological Society of America (SSA)} \textbar { 2020 - Present}} \\
     \textit{Member}{, Asociación Latinoamericana de Volcanología (ALVO)} \textbar { 2019 - Present} \\
     \textit{Member}{, Mexican Association of Exploration Geophysicists (AMGE)} \textbar { 2017 - Present} \\
    }
 \end{itemize}
 \vspace{-16pt}

\end{document}
